---
title: "LBB Data Visualization"
author: "Samsinar Ilyas"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Data Explanation 

Dataset on Amazon's Top 50 bestselling books from 2009 to 2019. Contains 550 books, data has been categorized into fiction and non-fiction using Goodreads

FEATURES:

- Name - Name of the Book
- Author - The author of the Book
- User Rating - Amazon User Rating
- Reviews - Number of written reviews on amazon
- Price - The price of the book (As at 13/10/2020)
- Year - The Year(s) it ranked on the bestseller
- Genre - Whether fiction or non-fiction

# 2. Input Data

At first, enable the library to use
```{r}
library(ggplot2)
library(ggthemes)
theme_algoritma <- readRDS("theme_algoritma.rds")
```

Read the data, make sure the data is in the sama place with R project.
```{r}
books <- read.csv("bestsellers with categories.csv")
head(books)
```

# 3. Data Mining

### Check for Missing Value
```{r}
anyNA(books)
```
### Check the type of data, change data type which is not appropriate
```{r}
str(books)
```

change the type date of `year` and `Genre`
```{r}
books$Year <- as.factor(books$Year)
books$Genre <- as.factor(books$Genre)
```

**Now, Data already to analysis!**


# 4. Exploratory Data Analysis and Data Visualization

### Check the summary of data
```{r}
summary(books)
```

## Comparison of Reviews by Genre 

```{r}


ggplot(books, aes(x = Year,
                        y = Reviews,
                        fill = Genre)
       ) +
  geom_boxplot() +
  scale_fill_brewer(palette = "Set1") +
  
  labs(title = "Comparison of Reviews by Genre",
       subtitle = "From 2009-2019",
       caption = "Dataset: Kaggle",
       x = "Year",
       y = "Reviews",
       color = "Genre" 
       ) +
  theme_algoritma

```

## Correlation of User Reviews and Ratings

```{r}
ggplot(books,
       aes(
         x = User.Rating,
         y = Reviews,
         size = Reviews,
         color = Genre,
         alpha = User.Rating
       ))+
  geom_point()+
  scale_color_brewer(palette = "Dark2")+
  
  labs(title = "Correlation of User Reviews and Ratings",
       subtitle = "Based on Genre",
       caption = "Dataset: Kaggle",
       x = "Reviews",
       y = "Ratings",
       color = "Genre",
       size = "Reviews",
       alpha = "Rating"
       ) +
  guides(size = F)+
  guides(alpha = F)+
  theme_algoritma
```

## The Most Reviewed Books Each Year

```{r}
#TOP BOOK BY REVIEW EVERY YEAR
top_book_review_year <- books[order(books$Reviews, decreasing = TRUE),]
top_book_review_year <- top_book_review_year[ match(x = unique(top_book_review_year$Year), table = top_book_review_year$Year), ]
```

```{r}
ggplot(top_book_review_year,
       aes(
         x = Year,
         y = Name,
       ))+
  geom_col(fill = "turquoise4")+
  
  labs(
    title = "The Most Reviewed Books Each Year",
    x = "",
    y = "")+
  
  theme_algoritma
```

## Top 10 Book Based on Reviews

```{r}
top_book_review <- books[order(books$Reviews, decreasing = TRUE),]
top_book_review <- top_book_review[ match(x = unique(top_book_review$Name), table = top_book_review$Name), ]
top_book_review <- head(top_book_review, 10)
```

```{r}
ggplot(top_book_review,
       aes(
         x = Reviews,
         y = reorder(Name, Reviews),
       ))+
  geom_col(fill = "turquoise4")+
  
  labs(
    title = "Top 10 Book Based on Reviews",
    x = "",
    y = "")+
  
  theme_algoritma
```

## Top 10 Book Based on Ratings

```{r}
#TOP BOOK BY RATING
top_book_rating <- books[order(books$User.Rating, decreasing = TRUE),]
top_book_rating <- top_book_rating[ match(x = unique(top_book_rating$Name), table = top_book_rating$Name), ]
top_book_rating <- head(top_book_rating, 10)
```

```{r}
ggplot(top_book_rating,
       aes(
         x = User.Rating,
         y = reorder(Name, User.Rating),
       ))+
  geom_col(fill = "turquoise4")+
  
  labs(
    title = "Top 10 Book Based on Ratings",
    x = "",
    y = "")+
  
  theme_algoritma
```


## Top 10 Author Based on Reviews

```{r}
top_author <- books[order(books$Reviews, decreasing = TRUE),]
top_author <- top_author[ match(x = unique(top_author$Author), table = top_author$Author), ]
top_author <- head(top_author, 10)
```

```{r}
ggplot(top_author,
       aes(
         x = Reviews,
         y = reorder(Author, Reviews),
       ))+
  geom_col(fill = "turquoise4")+
  
  labs(
    title = "Top 10 Author Based on Reviews",
    x = "",
    y = "")+
  
  theme_algoritma
```

## Top 10 Author Based on Ratings

```{r}
top_author1 <- books[order(books$User.Rating, decreasing = TRUE),]
top_author1 <- top_author1[ match(x = unique(top_author1$Author), table = top_author1$Author), ]
top_author1 <- head(top_author1, 10)
```


```{r}
ggplot(top_author1,
       aes(
         x = User.Rating,
         y = reorder(Author, User.Rating),
       ))+
  geom_col(fill = "turquoise4")+
  
  labs(
    title = "Top 10 Author Based on Ratings",
    x = "",
    y = "")+
  
  theme_algoritma
```


## Histogram of Prices

```{r}
ggplot(books,
  aes(
    x = Price)
  )+
  
  geom_histogram(fill = "turquoise4")+
  
  labs(title = "Histogram of Prices")+
  
  theme_algoritma

```





